%______________________________________________________________________________________________________________________
% Parametric resume — example persona "Alex Rivera", Software Engineer
% All content choices are controlled by named variables injected at compile time.
% Build via the configurator command, build.sh, or compile.sh. Compiles standalone too (defaults apply).
%
% The persona is intentionally ONE coherent person: a backend-leaning full-stack
% engineer. Variants reframe the same underlying work with a different emphasis
% (systems/performance vs. product delivery) — they never invent a different career.
%
% ===== VARIABLES =====
% \biover      — bio version: general | systems | product
% \layout      — resume structure:
%                  threeroles — Experience (both jobs + internship), Education, Skills
%                  research   — Industry Experience, Portfolio Project, Research Experience, Education, Skills
%                  portfolio  — Experience (both jobs), Portfolio Project, Education, Skills
% \teamlabel   — free-text team name in the current-role header
% \showcert    — true/false: show Certifications section
%
% Job A (Northwind Analytics) bullets — max 3:
%   \jaone   streaming | dashboards | leadership   — same launch, three framings
%   \jatwo   latency | reliability
%   \jathree mentoring | tooling | hide            — optional third bullet (default hide)
%
% Job B (Lakeshore Labs) bullets — max 3 (third is fixed):
%   \jbone   fullstack | metering
%   \jbtwo   migration | testing
%
% Internship (Harborview Systems) — 2 bullets (second is fixed):
%   \inone   logsearch | releasenotes
%
% Research role (Data Systems Lab) — 2 bullets (second is fixed):
%   \rone    harness | paper
%
% Portfolio project:
%   \projfocus systems | product                   — swaps framing of project bullets 1 & 3
%
% Skills:
%   \sline   gofirst | tsfirst                     — ordering of the Languages line
%
% Skill group visibility (true / false):
%   \showsys    — Systems & Infrastructure (default true)
%   \showweb    — Product & Web (default true)
%   \showcomm   — Collaboration (default false)
%   \showprog   — Languages (default true)
%   \showoncall — inline: appends Incident Response & On-Call to the Systems line (default true)
% ================================================================

\ifx\biover\undefined\def\biover{general}\fi
\ifx\layout\undefined\def\layout{threeroles}\fi
\ifx\teamlabel\undefined\def\teamlabel{Platform}\fi
\ifx\showcert\undefined\def\showcert{false}\fi
\ifx\jaone\undefined\def\jaone{streaming}\fi
\ifx\jatwo\undefined\def\jatwo{latency}\fi
\ifx\jathree\undefined\def\jathree{hide}\fi
\ifx\jbone\undefined\def\jbone{fullstack}\fi
\ifx\jbtwo\undefined\def\jbtwo{migration}\fi
\ifx\inone\undefined\def\inone{logsearch}\fi
\ifx\rone\undefined\def\rone{harness}\fi
\ifx\projfocus\undefined\def\projfocus{systems}\fi
\ifx\sline\undefined\def\sline{gofirst}\fi
\ifx\showsys\undefined\def\showsys{true}\fi
\ifx\showweb\undefined\def\showweb{true}\fi
\ifx\showcomm\undefined\def\showcomm{false}\fi
\ifx\showprog\undefined\def\showprog{true}\fi
\ifx\showoncall\undefined\def\showoncall{true}\fi

% Value anchors for \ifx comparisons (zero stray tokens when a condition is false).
% Anchor names must be letters only; values may contain digits.
\def\Vtrue{true}
\def\Vthreeroles{threeroles}
\def\Vresearch{research}
\def\Vportfolio{portfolio}
\def\Vstreaming{streaming}
\def\Vdashboards{dashboards}
\def\Vleadership{leadership}
\def\Vlatency{latency}
\def\Vreliability{reliability}
\def\Vmentoring{mentoring}
\def\Vtooling{tooling}
\def\Vfullstack{fullstack}
\def\Vmetering{metering}
\def\Vmigration{migration}
\def\Vtesting{testing}
\def\Vlogsearch{logsearch}
\def\Vreleasenotes{releasenotes}
\def\Vharness{harness}
\def\Vpaper{paper}
\def\Vsystems{systems}
\def\Vproduct{product}
\def\Vgofirst{gofirst}
\def\Vtsfirst{tsfirst}

\renewenvironment{itemize}{
  \begin{list}{}{
  }
}{
  \end{list}%
}

\documentclass{resume}
\usepackage{enumitem}
\usepackage{etoolbox}
% Tighten the class's inter-section spacing (default \bigskip) so every
% variant fits one page. Remove or change to taste.
\renewcommand{\sectionskip}{\smallskip}
\usepackage{fontawesome}
\usepackage[left=0.4in,top=0.2in,right=0.5in,bottom=0.2in]{geometry}
\usepackage{hyperref}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\name{Alex Rivera}
% Note: keep the header links plain text. The class prints this block in an
% \AtBeginDocument hook that runs before hyperref is initialized, so \href
% here breaks the build. \href works fine in the document body.
\address{\footnotesize \faEnvelope~alex.rivera@example.com \quad \faLinkedin~linkedin.com/in/alex-rivera-example \quad \faGithub~github.com/alexrivera-example \quad \faPhone~555-555-0123}

%--------------------------------------------------
% ROLE BLOCKS
% Each role is defined ONCE as a macro; the layout switch below assembles them.
% (Bullet conditionals expand when the macro is used, so \ifx works normally.)
%--------------------------------------------------

\newcommand{\NorthwindBlock}{%
\hspace{-0.2in}  \textbf{Software Engineer,  Northwind Analytics}, \teamlabel{} team, Chicago, IL \hfill 03/2023--Present
\begin{itemize}[leftmargin=0.2in]    \setlength\itemsep{-0.2em}
{\small
\ifx\jaone\Vstreaming\item Redesigned the ingestion service behind customer dashboards, moving from batch polling to a streaming pipeline (Kafka, Go) and cutting data freshness from 15 minutes to under 30 seconds at 20K events/sec.\fi
\ifx\jaone\Vdashboards\item Led engineering for the real-time dashboards launch, the company's most-requested feature, partnering with design and product from prototype through GA for 800+ customer accounts.\fi
\ifx\jaone\Vleadership\item Owned the real-time dashboards initiative end to end: scoped the rollout with product, coordinated two other engineers, and shipped the streaming backend that took data freshness from 15 minutes to under 30 seconds.\fi
\ifx\jatwo\Vlatency\item Cut p99 API latency 60\% by profiling hot paths, adding query-level caching, and rewriting the database access patterns of the two worst-offending endpoints.\fi
\ifx\jatwo\Vreliability\item Drove the reliability push that took the platform from 99.5\% to 99.95\% uptime: defined SLOs, added load-shedding, and rewrote the on-call runbook, halving weekly pages.\fi
\ifx\jathree\Vmentoring\item Mentored two interns and a new-grad engineer through their first production launches; wrote the onboarding guide now used across the organization.\fi
\ifx\jathree\Vtooling\item Built internal CLI tooling for service scaffolding and deploy previews, adopted by all six backend teams.\fi
}
\end{itemize}
{\small \textbf{Tech Stack:} Go, TypeScript, Kafka, Postgres, Redis, Kubernetes, Grafana}\par\smallskip
}

\newcommand{\LakeshoreBlock}{%
\hspace{-0.2in}  \textbf{Software Engineer,  Lakeshore Labs}, Chicago, IL \hfill 07/2020--03/2023
\begin{itemize}[leftmargin=0.2in]    \setlength\itemsep{-0.2em}
{\small
\ifx\jbone\Vfullstack\item Shipped the customer-facing usage-analytics feature end to end (React, TypeScript, Node.js), which became a top-three driver of enterprise renewals.\fi
\ifx\jbone\Vmetering\item Built the metering and usage-aggregation service (Node.js, Postgres) behind customer-facing analytics, processing 5M events per day with exactly-once semantics.\fi
\ifx\jbtwo\Vmigration\item Led the migration from a legacy cron-based monolith to containerized workers on Kubernetes, cutting deploy time from 45 minutes to 5 and enabling per-service scaling.\fi
\ifx\jbtwo\Vtesting\item Introduced contract testing and CI gates across three services, roughly halving production incidents caused by integration bugs.\fi
\item Interviewed and onboarded engineers as the team grew from 4 to 11.
}
\end{itemize}
{\small \textbf{Tech Stack:} TypeScript, Node.js, React, Postgres, Docker, Kubernetes}\par\smallskip
}

\newcommand{\InternBlock}{%
\hspace{-0.2in}  \textbf{Software Engineering Intern,  Harborview Systems}, Seattle, WA \hfill 06/2019--09/2019
\begin{itemize}[leftmargin=0.2in]    \setlength\itemsep{-0.2em}
{\small
\ifx\inone\Vlogsearch\item Built an indexed log-search web tool for the support team, replacing grep-over-SSH and cutting median ticket investigation time by half.\fi
\ifx\inone\Vreleasenotes\item Automated release-notes generation from merged pull requests, saving the team several hours per release and standardizing changelog quality.\fi
\item Shipped to production before the internship ended; received and accepted a return offer for a final-year part-time role.
}
\end{itemize}
{\small \textbf{Tech Stack:} Python, Elasticsearch, Flask}\par\smallskip
}

\newcommand{\ResearchBlock}{%
\hspace{-0.2in}  \textbf{Research Assistant,  Data Systems Lab}, State University \hfill 09/2018--06/2020
\begin{itemize}[leftmargin=0.2in]    \setlength\itemsep{-0.2em}
{\small
\ifx\rone\Vharness\item Built the benchmarking harness for the lab's query-optimization research, running 10K+ experiment configurations reproducibly on a shared cluster.\fi
\ifx\rone\Vpaper\item Co-authored a workshop paper on adaptive query optimization; implemented the prototype and ran all experiments.\fi
\item Maintained the lab's shared experiment infrastructure used by six graduate students.
}
\end{itemize}
{\small \textbf{Tech Stack:} C++, Python, Slurm, Linux}\par\smallskip
}

\newcommand{\ProjectSection}{%
\begin{rSection}{Portfolio Project}
\hspace{-0.2in} Transit Delay Tracker — open-source project (2025) \hfill \href{https://github.com/alexrivera-example/transit-tracker}{github.com/alexrivera-example/transit-tracker}
{\small
\begin{itemize}[leftmargin=0.2in]    \setlength\itemsep{-0.2em}
\ifx\projfocus\Vsystems\item Built a Go service ingesting live transit feeds (2M+ records/day) with Redis caching and Postgres storage, running with full observability on a \$5/month VPS.\fi
\ifx\projfocus\Vproduct\item Built and launched a web app answering a real commuter question, ``should I leave now or wait?'', from live transit feeds; 1,200 weekly users and a public API.\fi
\item Wrote the data pipeline handling schedule changes and feed outages; open source with CI and a reproducible local setup.
\ifx\projfocus\Vsystems\item Load-tested and tuned the ingestion path to absorb 10x feed bursts during citywide service disruptions.\fi
\ifx\projfocus\Vproduct\item Iterated the UI from user feedback collected in a public issue tracker; published a technical write-up of the architecture.\fi
\end{itemize}
}
\small{\textbf{Tech Stack:} Go, Redis, Postgres, React, GitHub Actions}
\end{rSection}
}

\newcommand{\EducationSection}{%
\begin{rSection}{Education}
\hspace{-0.2in}  \textbf{BS in Computer Science}, State University \hfill 2020\\ \vspace{-0.25in}
\begin{itemize}[leftmargin=0.2in]
{\small\item Undergraduate research in the Data Systems Lab; teaching assistant for the databases course.}
\end{itemize}
\end{rSection}
}

\begin{document}

%--------------------------------------------------
% BIO
% Bio conditionals intentionally use \ifdefstring (etoolbox), not \ifx:
% paragraph mode tolerates the empty {} group of the false branch.
%--------------------------------------------------
\begin{rSection}{Bio}
\ifdefstring{\biover}{general}{%
\small{Software engineer with five years of experience building backend services and the product features on top of them. Comfortable owning a feature from API design through frontend delivery, with a track record of improving reliability and performance along the way.}%
}{}%
\ifdefstring{\biover}{systems}{%
\small{Software engineer specializing in backend systems and data infrastructure: high-throughput APIs, streaming pipelines, and the observability that keeps them reliable. Cut latency, incident load, and infrastructure costs on services handling millions of requests per day.}%
}{}%
\ifdefstring{\biover}{product}{%
\small{Product-minded software engineer who ships user-facing features end to end, from API design to frontend polish, in close collaboration with design and product. Known for fast, well-instrumented launches that hold up under real traffic.}%
}{}%
\end{rSection}

%--------------------------------------------------
% LAYOUT SWITCH — assembles the role blocks defined above
%--------------------------------------------------
\ifx\layout\Vresearch

%--- RESEARCH: industry, project, research, education ---
\begin{rSection}{Industry Experience}
\NorthwindBlock
\LakeshoreBlock
\end{rSection}
\ProjectSection
\begin{rSection}{Research Experience}
\ResearchBlock
\end{rSection}
\EducationSection

\else\ifx\layout\Vportfolio

%--- PORTFOLIO: experience, project, education ---
\begin{rSection}{Experience}
\NorthwindBlock
\LakeshoreBlock
\end{rSection}
\ProjectSection
\EducationSection

\else

%--- THREEROLES (default): experience with both jobs + internship, education ---
\begin{rSection}{Experience}
\NorthwindBlock
\LakeshoreBlock
\InternBlock
\end{rSection}
\EducationSection

\fi\fi% end layout switch

%--------------------------------------------------
% CERTIFICATIONS
%--------------------------------------------------
\ifx\showcert\Vtrue
\begin{rSection}{Certifications}
\hspace{-0.2in} \textbf{AWS Certified Solutions Architect — Associate} \hfill 2023
\end{rSection}
\fi

%--------------------------------------------------
% SKILLS (appears once — after the layout switch)
%--------------------------------------------------
\begin{rSection}{Skills \& Expertise}
{\small
\ifx\showsys\Vtrue
\textbf{Systems \& Infrastructure}: Kafka; Kubernetes; Redis; gRPC; Observability (Prometheus, Grafana); Performance \& Load Testing; CI/CD\ifx\showoncall\Vtrue{; Incident Response \& On-Call}\fi\vspace{-0.05in}

\fi
\ifx\showweb\Vtrue
\textbf{Product \& Web}: React; TypeScript; Node.js; REST \& GraphQL API Design; Instrumentation \& Feature-Flag Rollouts\vspace{-0.05in}

\fi
\ifx\showcomm\Vtrue
\textbf{Collaboration}: Design Partnership; Mentoring; Technical Writing; Interviewing \& Onboarding\vspace{-0.05in}

\fi
\ifx\showprog\Vtrue
\ifx\sline\Vgofirst
\textbf{Languages}: Go, TypeScript, Python, SQL, C++
\fi
\ifx\sline\Vtsfirst
\textbf{Languages}: TypeScript, JavaScript, Go, Python, SQL
\fi
\fi
}
\end{rSection}

\end{document}
